---
title: "Organic Food Environment Assessment"
author: "Alexandra Sadler"
date: "19/07/2024"
output: word_document
---

```{r setup, include=FALSE}
# Load necessary libraries
library(dplyr)
library(gmodels)
library(gt)
library(knitr)
library(kableExtra)
library(openxlsx)
library(readxl)
library(readr)
library(stats)
library(tidyr)

knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}

# Set working directory
#setwd("C:/Users/s1985751/Documents/GitHub/fea")


# Load cleaned data
data_clean <- read.xlsx("data_clean.xlsx", sheet = "data")

# Create workbook for table data
table_outputs <- createWorkbook()
saveWorkbook(table_outputs, "Outputs/table_outputs.xlsx", overwrite = TRUE)


```

## Descriptive Results

### Table 1

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Generate Table 1

# Calculate total vendors per city
tab1_total_vendors <- data_clean %>%
  group_by(country, city) %>%
  summarise(total_vendors = n()) %>%
  ungroup()

# Calculate neighbourhood counts and percentages
tab1_neighbourhood_data <- data_clean %>%
  group_by(country, city, circle) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = circle, values_from = count, values_fill = list(count = 0)) %>%
  ungroup() %>%
  left_join(tab1_total_vendors, by = c("country", "city")) %>%
  mutate(
    higher_perc = Higher / total_vendors,
    middle_perc = Middle / total_vendors,
    lower_perc = Lower / total_vendors
  ) %>%
  select(country, city, total_vendors, Higher, higher_perc, Middle, middle_perc, Lower, lower_perc)

# Calculate store type counts and percentages
tab1_store_data <- data_clean %>%
  group_by(country, city, vendor_type) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = vendor_type, values_from = count, values_fill = list(count = 0)) %>%
  ungroup() %>%
  left_join(tab1_total_vendors, by = c("country", "city")) %>%
  mutate(
    supermarket_perc = Supermarket / total_vendors,
    mobile_vendor_perc = `Mobile vendor` / total_vendors,
    stationary_small_vendor_perc = `Stationary small local vendor` / total_vendors
  ) %>%
  select(country, city, `Mobile vendor`, mobile_vendor_perc, `Stationary small local vendor`, stationary_small_vendor_perc, Supermarket, supermarket_perc,  )


# Merge both datasets
tab1_data <- tab1_neighbourhood_data %>%
  left_join(tab1_store_data, by = c("country", "city"))


# Create the gt table
tab1 <- tab1_data %>%
  gt(rowname_col = "city", groupname_col = "country") %>%
  cols_label(
    city = "City",
    total_vendors = "Total vendors",
    Higher = "Higher",
    higher_perc = " ",
    Middle = "Middle",
    middle_perc = " ",
    Lower = "Lower",
    lower_perc = " ",
    `Mobile vendor` = "Mobile vendor",
    mobile_vendor_perc = " ",
    `Stationary small local vendor` = "Stationary small vendor",
    stationary_small_vendor_perc = " ",
    Supermarket = "Supermarket",
    supermarket_perc = " "
  ) %>%
  fmt_percent(
    columns = vars(higher_perc, middle_perc, lower_perc,
                   mobile_vendor_perc, stationary_small_vendor_perc,
                   supermarket_perc),
    decimals = 0
  ) %>%
  cols_merge(
    columns = c("Higher", "higher_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("Middle", "middle_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("Lower", "lower_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("Mobile vendor", "mobile_vendor_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("Stationary small local vendor",
                "stationary_small_vendor_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("Supermarket", "supermarket_perc"),
    pattern = "{1} ({2})"
  ) %>%
  summary_rows(
    groups = everything(),
    columns = vars(total_vendors, Higher, higher_perc,
                   Middle, middle_perc,
                   Lower, lower_perc, 
                   `Mobile vendor`, mobile_vendor_perc,
                   `Stationary small local vendor`,
                   stationary_small_vendor_perc,
                   Supermarket, supermarket_perc),
    fns = list(total = ~sum(., na.rm = TRUE)),
    formatter = fmt_number,
    decimals = 0
  ) %>%
  grand_summary_rows(
    columns = vars(total_vendors, Higher, higher_perc,
                   Middle, middle_perc,
                   Lower, lower_perc, 
                   `Mobile vendor`, mobile_vendor_perc,
                   `Stationary small local vendor`,
                   stationary_small_vendor_perc,
                   Supermarket, supermarket_perc),
    fns = list(total = ~sum(., na.rm = TRUE)),
    formatter = fmt_number,
    decimals = 0
  ) %>%
  sub_missing() 
  
# Display the table
tab1

# Note: I can't seem to get it to also have the percentage columns
# Note: Also don't know how to do a grand total - keep getting errors

# Export to table_outputs workbook

addWorksheet(table_outputs, "Table 1")
writeData(table_outputs, sheet = "Table 1", x = tab1)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)


```



## 1. What is the availability of organic food in urban food environments? How does this vary across different geographic and socioeconomic contexts?

### Hypothesis 1a. Organic food availability will be highest in the United Kingdom, in larger cities within a given country, and in higher-income neighbourhoods within a given city.

#### Kruskal-Wallis rank sum test

##### Overall results (variation between countries)
```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame of country and org_foods_count
kruskal_country_data <- data_clean %>%
  select(country, org_foods_count)

# Perform the Kruskal-Wallis test
result_overall <- kruskal.test(org_foods_count ~ country, data = kruskal_country_data)
  
# Display the results
print(result_overall)

```

##### Country-level results (variation between cities within a given country)

###### Brazil

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame for Brazil
brazil <- data_clean %>%
  filter(country == "Brazil")

# Create data frame of city and org_foods_count
kruskal_brazil_city_data <- brazil %>%
  select(city, org_foods_count)

# Perform the Kruskal-Wallis test
result_brazil <- kruskal.test(org_foods_count ~ city, data = kruskal_brazil_city_data)
  
# Display the results
print(result_brazil)

```

###### India

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame for India
india <- data_clean %>%
  filter(country == "India")

# Create data frame of city and org_foods_count
kruskal_india_city_data <- india %>%
  select(city, org_foods_count)

# Perform the Kruskal-Wallis test
result_india <- kruskal.test(org_foods_count ~ city, data = kruskal_india_city_data)
  
# Display the results
print(result_india)

```

###### United Kingdom

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame for India
uk <- data_clean %>%
  filter(country == "UK")

# Create data frame of city and org_foods_count
kruskal_uk_city_data <- uk %>%
  select(city, org_foods_count)

# Perform the Kruskal-Wallis test
result_uk <- kruskal.test(org_foods_count ~ city, data = kruskal_uk_city_data)
  
# Display the results
print(result_uk)

```

##### City-level results (variation between neighbourhoods within a given city)

###### Brazil: Rio de Janeiro

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame for Rio de Janeiro
rio <- data_clean %>%
  filter(city == "Rio de Janeiro")

# Create data frame of circle and org_foods_count
kruskal_rio_data <- rio %>%
  select(circle, org_foods_count)

# Perform the Kruskal-Wallis test
result_rio <- kruskal.test(org_foods_count ~ circle, data = kruskal_rio_data)
  
# Display the results
print(result_rio)

```

###### Brazil: Sao Paulo

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame for Sao Paulo
saopaulo <- data_clean %>%
  filter(city == "Sao Paolo")

# Create data frame of circle and org_foods_count
kruskal_saopaulo_data <- saopaulo %>%
  select(circle, org_foods_count)

# Perform the Kruskal-Wallis test
result_saopaulo <- kruskal.test(org_foods_count ~ circle, data = kruskal_saopaulo_data)
  
# Display the results
print(result_saopaulo)

```

###### Brazil: Sinop

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame for Sinop
sinop <- data_clean %>%
  filter(city == "Sinop")

# Create data frame of circle and org_foods_count
kruskal_sinop_data <- sinop %>%
  select(circle, org_foods_count)

# Perform the Kruskal-Wallis test
result_sinop <- kruskal.test(org_foods_count ~ circle, data = kruskal_sinop_data)
  
# Display the results
print(result_sinop)

```


###### India: Hyderabad

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame for Hyderabad
hyderabad <- data_clean %>%
  filter(city == "Hyderabad")

# Create data frame of circle and org_foods_count
kruskal_hyderabad_data <- hyderabad %>%
  select(circle, org_foods_count)

# Perform the Kruskal-Wallis test
result_hyderabad <- kruskal.test(org_foods_count ~ circle, data = kruskal_hyderabad_data)
  
# Display the results
print(result_hyderabad)

```

###### India: Latur

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame for Latur
latur <- data_clean %>%
  filter(city == "Latur")

# Create data frame of circle and org_foods_count
kruskal_latur_data <- latur %>%
  select(circle, org_foods_count)

# Perform the Kruskal-Wallis test
result_latur <- kruskal.test(org_foods_count ~ circle, data = kruskal_latur_data)
  
# Display the results
print(result_latur)

```

###### India: Visakhapatnam

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame for Visakhapatnam
visakhapatnam <- data_clean %>%
  filter(city == "Visakhapatnam")

# Create data frame of circle and org_foods_count
kruskal_visakhapatnam_data <- visakhapatnam %>%
  select(circle, org_foods_count)

# Perform the Kruskal-Wallis test
result_visakhapatnam <- kruskal.test(org_foods_count ~ circle, data = kruskal_visakhapatnam_data)
  
# Display the results
print(result_visakhapatnam)

```

###### United Kingdom: Birmingham

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame for Birmingham
birmingham <- data_clean %>%
  filter(city == "Birmingham")

# Create data frame of circle and org_foods_count
kruskal_birmingham_data <- birmingham %>%
  select(circle, org_foods_count)

# Perform the Kruskal-Wallis test
result_birmingham <- kruskal.test(org_foods_count ~ circle, data = kruskal_birmingham_data)
  
# Display the results
print(result_birmingham)

```

###### UK: Edinburgh

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame for Edinburgh
edinburgh <- data_clean %>%
  filter(city == "Edinburgh")

# Create data frame of circle and org_foods_count
kruskal_edinburgh_data <- edinburgh %>%
  select(circle, org_foods_count)

# Perform the Kruskal-Wallis test
result_edinburgh <- kruskal.test(org_foods_count ~ circle, data = kruskal_edinburgh_data)
  
# Display the results
print(result_edinburgh)

```

###### UK: London

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame for London
london <- data_clean %>%
  filter(city == "London")

# Create data frame of circle and org_foods_count
kruskal_london_data <- london %>%
  select(circle, org_foods_count)

# Perform the Kruskal-Wallis test
result_london <- kruskal.test(org_foods_count ~ circle, data = kruskal_london_data)
  
# Display the results
print(result_london)

```

##### Summary of p-values

###### Overall p-value

```{r echo = FALSE, message = FALSE, warning = FALSE}

p_values_kruskal_overall <- result_overall$p.value

print(p_values_kruskal_overall)
```


###### Country-level p-values
```{r echo = FALSE, message = FALSE, warning = FALSE, results = 'hide'}

# Create a vector of country names
country_names <- c("Brazil","India","UK")

# Create a vector of the result object names
kruskal_country_result_names <- c("result_brazil", "result_india", "result_uk")

# Retrieve results and store in a list
kruskal_country_result_list <- mget(kruskal_country_result_names)

# Print list to confirm
print(kruskal_country_result_list)

# Extract p-values from the results
p_values_kruskal_country <- sapply(kruskal_country_result_list, function(res) res$p.value)

# Create a dataframe
p_values_kruskal_country_df <- data.frame(
  Country = country_names,
  PValue = p_values_kruskal_country
)

print(p_values_kruskal_country_df)

```

###### City-level p-values

```{r echo = FALSE, message = FALSE, warning = FALSE, results = 'hide'}

# Create a vector of city names
city_names <- c("Rio de Janeiro","Sao Paolo","Sinop",
                "Hyderabad","Latur","Visakhapatnam",
                "Birmingham","Edinburgh","London")

# Create a vector of the result object names
kruskal_city_result_names <- c("result_rio","result_saopaulo","result_sinop",
                               "result_hyderabad","result_latur",
                               "result_visakhapatnam","result_birmingham",
                               "result_edinburgh","result_london")

# Retrieve results and store in a list
kruskal_city_result_list <- mget(kruskal_city_result_names)

# Print list to confirm
print(kruskal_city_result_list)

# Extract p-values from the results
p_values_kruskal_city <- sapply(kruskal_city_result_list, function(res) res$p.value)

# Create a dataframe
p_values_kruskal_city_df <- data.frame(
  City = city_names,
  PValue = p_values_kruskal_city
)

print(p_values_kruskal_city_df)


```


#### Chi-squared test

##### Overall results (variation between countries)
```{r echo = FALSE, message = FALSE, warning = FALSE}
# Prepare a contingency table
contingency_table <- data_clean %>%
  group_by(country, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$country

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_overall <- chisq.test(data_matrix)

# Display the results
print(chi_result_overall)

```

##### Country-level results (variation between cities within a given country)

###### Brazil

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Prepare a contingency table
contingency_table <- brazil %>%
  group_by(city, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$city

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_brazil <- chisq.test(data_matrix)

# Display the results
print(chi_result_brazil)

```

###### India

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Prepare a contingency table
contingency_table <- india %>%
  group_by(city, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$city

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_india <- chisq.test(data_matrix)

# Display the results
print(chi_result_india)
```

###### United Kingdom

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Prepare a contingency table
contingency_table <- uk %>%
  group_by(city, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$city

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_uk <- chisq.test(data_matrix)

# Display the results
print(chi_result_uk)
```

##### Neighbourhood-level results (variation between neighbourhoods within a given city)

###### Brazil: Rio de Janeiro

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Prepare a contingency table
contingency_table <- rio %>%
  group_by(circle, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$circle

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_rio <- chisq.test(data_matrix)

# Display the results
print(chi_result_rio)

```


###### Brazil: Sao Paulo

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Prepare a contingency table
contingency_table <- saopaulo %>%
  group_by(circle, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$circle

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_saopaulo <- chisq.test(data_matrix)

# Display the results
print(chi_result_saopaulo)

```

###### Brazil: Sinop

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Prepare a contingency table
contingency_table <- sinop %>%
  group_by(circle, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$circle

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_sinop <- chisq.test(data_matrix)

# Display the results
print(chi_result_sinop)

```

###### India: Hyderabad

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Prepare a contingency table
contingency_table <- hyderabad %>%
  group_by(circle, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$circle

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_hyderabad <- chisq.test(data_matrix)

# Display the results
print(chi_result_hyderabad)

```

###### India: Latur

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Prepare a contingency table
contingency_table <- latur %>%
  group_by(circle, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$circle

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_latur <- chisq.test(data_matrix)

# Display the results
print(chi_result_latur)

```

###### India: Visakhapatnam

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Prepare a contingency table
contingency_table <- visakhapatnam %>%
  group_by(circle, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$circle

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_visakhapatnam <- chisq.test(data_matrix)

# Display the results
print(chi_result_visakhapatnam)
```

###### United Kingdom: Birmingham

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Prepare a contingency table
contingency_table <- birmingham %>%
  group_by(circle, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$circle

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_birmingham <- chisq.test(data_matrix)

# Display the results
print(chi_result_birmingham)

```

###### United Kingdom: Edinburgh

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Prepare a contingency table
contingency_table <- edinburgh %>%
  group_by(circle, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$circle

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_edinburgh <- chisq.test(data_matrix)

# Display the results
print(chi_result_edinburgh)

```

###### United Kingdom: London

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Prepare a contingency table
contingency_table <- london %>%
  group_by(circle, org_vendor) %>%
  tally() %>%
  pivot_wider(names_from = org_vendor, values_from = n, values_fill = list(n = 0))

# Convert to matrix 
data_matrix <- as.matrix(contingency_table[, -1])

# Set row names
rownames(data_matrix) <- contingency_table$circle

# Display the matrix to check if it's correct
print(data_matrix)

# Perform Chi-squared test
chi_result_london <- chisq.test(data_matrix)

# Display the results
print(chi_result_london)

```

##### Summary of p-values

###### Overall p-value

```{r echo = FALSE, message = FALSE, warning = FALSE}

p_values_chi_overall <- chi_result_overall$p.value

print(p_values_chi_overall)
```


###### Country-level p-values
```{r echo = FALSE, message = FALSE, warning = FALSE, results = 'hide'}

# Create a vector of country names
country_names <- c("Brazil","India","UK")

# Create a vector of the result object names
chi_country_result_names <- c("chi_result_brazil", "chi_result_india", "chi_result_uk")

# Retrieve results and store in a list
chi_country_result_list <- mget(chi_country_result_names)

# Print list to confirm
print(chi_country_result_list)

# Extract p-values from the results
p_values_chi_country <- sapply(chi_country_result_list, function(res) res$p.value)

# Create a dataframe
p_values_chi_country_df <- data.frame(
  Country = country_names,
  PValue = p_values_chi_country
)

print(p_values_chi_country_df)

```


###### City-level p-values

```{r echo = FALSE, message = FALSE, warning = FALSE, results = 'hide'}

# Create a vector of city names
city_names <- c("Rio de Janeiro","Sao Paolo","Sinop",
                "Hyderabad","Latur","Visakhapatnam",
                "Birmingham","Edinburgh","London")

# Create a vector of the result object names
chi_city_result_names <- c("chi_result_rio","chi_result_saopaulo",
                          "chi_result_sinop","chi_result_hyderabad",
                          "chi_result_latur","chi_result_visakhapatnam",
                          "chi_result_birmingham", "chi_result_edinburgh",
                          "chi_result_london")

# Retrieve results and store in a list
chi_city_result_list <- mget(chi_city_result_names)

# Print list to confirm
print(chi_city_result_list)

# Extract p-values from the results
p_values_chi_city <- sapply(chi_city_result_list, function(res) res$p.value)

# Create a dataframe
p_values_chi_city_df <- data.frame(
  City = city_names,
  PValue = p_values_chi_city
)

print(p_values_chi_city_df)


```


#### Table 2

##### For each neighbourhood within each city
```{r echo = FALSE, message = FALSE, warning = FALSE}

# Define order of neighbourhood variable
circle_order <- c("Higher","Middle","Lower")
  
# Convert the circle column to a factor with the specified levels
data_clean <- data_clean %>%
  mutate(circle = factor(circle, levels = circle_order))

# Median and IQR number of organic sentinel foods
tab2_neighbourhood_data <- data_clean %>%
  group_by(country, city, circle) %>%
  summarise(
    vendors = n(),
    count_org_vendors = sum(org_vendor == 1, na.rm = TRUE),
    org_vendor_perc = count_org_vendors / vendors,
    median_org_foods_count = median(org_foods_count, na.rm = TRUE),
    iqr_org_foods_count = IQR(org_foods_count, na.rm = TRUE)
  ) %>%
  ungroup()

print(tab2_neighbourhood_data)

# Create the gt table
tab2_neighbourhood <- tab2_neighbourhood_data %>%
  gt(rowname_col = "circle", groupname_col = c("country","city")) %>%
  cols_label(
    country = "Country",
    city = "City",
    circle = "Neighbourhood",
    vendors = "Total vendors",
    count_org_vendors = "Organic vendors, n(%)",
    org_vendor_perc = " ",
    median_org_foods_count = "Organic sentinel foods, median (IQR)",
    iqr_org_foods_count = " "
  ) %>%
  fmt_percent(
    columns = vars(org_vendor_perc),
    decimals = 0
  ) %>%
  cols_merge(
    columns = c("count_org_vendors", "org_vendor_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("median_org_foods_count", "iqr_org_foods_count"),
    pattern = "{1} ({2})"
  ) %>%
  summary_rows(
    groups = everything(),
    columns = vars(vendors, count_org_vendors, org_vendor_perc,
                   median_org_foods_count, iqr_org_foods_count),
    fns = list(total = ~sum(., na.rm = TRUE)),
    formatter = fmt_number,
    decimals = 0
  ) %>%
  sub_missing() 
  
# Display the table
tab2_neighbourhood

# Note: I can't seem to get it to also have the percentage columns in the summary
# Note: Also don't know how to do a grand total - keep getting errors


# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 2 - neighbourhood")
writeData(table_outputs, sheet = "Table 2 - neighbourhood", x = tab2_neighbourhood)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

# create a variable to check how results would change if adding NA to org_foods_count for non organic vendors
data_clean$org_foods_count2 <- as.numeric(data_clean$org_foods_count)
data_clean$org_foods_count2[data_clean$org_vendor %in% 0] <- NA

# check how results would change
data_clean %>%
  group_by(country, city, circle) %>%
  summarise(
    median_org_foods_count = median(org_foods_count2, na.rm = TRUE),
    iqr_org_foods_count = IQR(org_foods_count2, na.rm = TRUE)
  )
```

##### For each city within each country
```{r echo = FALSE, message = FALSE, warning = FALSE}
# N, %, median and IQR - city level
tab2_city_data <- data_clean %>%
  group_by(country, city) %>%
  summarize(
    vendors = n(),
    count_org_vendors = sum(org_vendor == 1, na.rm = TRUE),
    org_vendor_perc = count_org_vendors / vendors,
    median_org_foods_count = median(org_foods_count, na.rm = TRUE),
    iqr_org_foods_count = IQR(org_foods_count, na.rm = TRUE)
  ) %>%
  ungroup()

print(tab2_city_data)


# Create the gt table
tab2_city <- tab2_city_data %>%
  gt(rowname_col = "city", groupname_col = c("country")) %>%
  cols_label(
    country = "Country",
    city = "City",
    vendors = "Total vendors",
    count_org_vendors = "Organic vendors, n(%)",
    org_vendor_perc = " ",
    median_org_foods_count = "Organic sentinel foods, median (IQR)",
    iqr_org_foods_count = " "
  ) %>%
  fmt_percent(
    columns = vars(org_vendor_perc),
    decimals = 0
  ) %>%
  cols_merge(
    columns = c("count_org_vendors", "org_vendor_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("median_org_foods_count", "iqr_org_foods_count"),
    pattern = "{1} ({2})"
  ) %>%
  summary_rows(
    groups = everything(),
    columns = vars(vendors, count_org_vendors, org_vendor_perc,
                   median_org_foods_count, iqr_org_foods_count),
    fns = list(total = ~sum(., na.rm = TRUE)),
    formatter = fmt_number,
    decimals = 0
  ) %>%
  sub_missing() 
  
# Display the table
tab2_city

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 2 - city")
writeData(table_outputs, sheet = "Table 2 - city", x = tab2_city)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```

##### For each country
```{r echo = FALSE, message = FALSE, warning = FALSE}
# N, %, median and IQR - country level
tab2_country_data <- data_clean %>%
  group_by(country) %>%
  summarize(
    vendors = n(),
    count_org_vendors = sum(org_vendor == 1, na.rm = TRUE),
    org_vendor_perc = count_org_vendors / vendors,
    median_org_foods_count = median(org_foods_count, na.rm = TRUE),
    iqr_org_foods_count = IQR(org_foods_count, na.rm = TRUE)
  ) %>%
  ungroup()

# Print output
print(tab2_country_data)

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 2 - country")
writeData(table_outputs, sheet = "Table 2 - country", x = tab2_country_data)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```

##### Overall
```{r echo = FALSE, message = FALSE, warning = FALSE}
# N, %, median and IQR - country level
tab2_overall <- data_clean %>%
  summarize(
    vendors = n(),
    count_org_vendors = sum(org_vendor == 1, na.rm = TRUE),
    org_vendor_perc = count_org_vendors / vendors,
    median_org_foods_count = median(org_foods_count, na.rm = TRUE),
    iqr_org_foods_count = IQR(org_foods_count, na.rm = TRUE)
  ) %>%
  ungroup()

# Print
print(tab2_overall)

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 2 - overall")
writeData(table_outputs, sheet = "Table 2 - overall", x = tab2_overall)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```


### Exploratory Analysis: Hypothesis 1b. The count and proportion of vendors selling multiple organic options for at least one sentinel food will be highest in the United Kingdom, in larger cities within a given country, and in higher-income neighbourhoods within a given city.


#### Table 3

##### For each neighbourhood within each city
```{r echo = FALSE, message = FALSE, warning = FALSE}
# N, %, median and IQR - neighbourhood level
tab3_neighbourhood_data <- data_clean %>%
  group_by(country, city, circle) %>%
  summarize(
    organic_vendors = sum(org_vendor == 1, na.rm = TRUE),
    n_multiple_org_binary = sum(multiple_org_binary == 1, na.rm = TRUE),
    perc_multiple_org_binary = n_multiple_org_binary / organic_vendors,
    median_multiple_org_count = median(multiple_org_count, na.rm = TRUE),
    iqr_multiple_org_count = IQR(multiple_org_count, na.rm = TRUE)
  ) %>%
  ungroup()

# Create the gt table
tab3_neighbourhood <- tab3_neighbourhood_data %>%
  gt(rowname_col = "circle", groupname_col = c("country","city")) %>%
  cols_label(
    country = "Country",
    city = "City",
    circle = "Neighbourhood",
    n_multiple_org_binary = "Organic vendors with multiple options (>1 product), n(%)",
    perc_multiple_org_binary = " ",
    median_multiple_org_count = "Foods with multiple options, median (IQR)",
    iqr_multiple_org_count = " "
  ) %>%
  fmt_percent(
    columns = vars(perc_multiple_org_binary),
    decimals = 0
  ) %>%
  cols_merge(
    columns = c("n_multiple_org_binary", "perc_multiple_org_binary"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("median_multiple_org_count", "iqr_multiple_org_count"),
    pattern = "{1} ({2})"
  ) %>%
  sub_missing() 
  
# Display the table
tab3_neighbourhood

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 3 - neighbourhood")
writeData(table_outputs, sheet = "Table 3 - neighbourhood", x = tab3_neighbourhood)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```

##### For each city within each country
```{r echo = FALSE, message = FALSE, warning = FALSE}
# N, %, median and IQR - city level
tab3_city_data <- data_clean %>%
  group_by(country, city) %>%
  summarize(
    organic_vendors = sum(org_vendor == 1, na.rm = TRUE),
    n_multiple_org_binary = sum(multiple_org_binary == 1, na.rm = TRUE),
    perc_multiple_org_binary = n_multiple_org_binary / organic_vendors,
    median_multiple_org_count = median(multiple_org_count, na.rm = TRUE),
    iqr_multiple_org_count = IQR(multiple_org_count, na.rm = TRUE)
  ) %>%
  ungroup()

# Create the gt table
tab3_city <- tab3_city_data %>%
  gt(rowname_col = "city", groupname_col = "country") %>%
  cols_label(
    country = "Country",
    city = "City",
    n_multiple_org_binary = "Organic vendors with multiple options (>1 product), n(%)",
    perc_multiple_org_binary = " ",
    median_multiple_org_count = "Foods with multiple options, median (IQR)",
    iqr_multiple_org_count = " "
  ) %>%
  fmt_percent(
    columns = vars(perc_multiple_org_binary),
    decimals = 0
  ) %>%
  cols_merge(
    columns = c("n_multiple_org_binary", "perc_multiple_org_binary"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("median_multiple_org_count", "iqr_multiple_org_count"),
    pattern = "{1} ({2})"
  ) %>%
  sub_missing() 
  
# Display the table
tab3_city

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 3 - city")
writeData(table_outputs, sheet = "Table 3 - city", x = tab3_city)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)
```

##### For each country
```{r echo = FALSE, message = FALSE, warning = FALSE}
# N, %, median and IQR - country level
tab3_country_data <- data_clean %>%
  group_by(country) %>%
  summarize(
    organic_vendors = sum(org_vendor == 1, na.rm = TRUE),
    n_multiple_org_binary = sum(multiple_org_binary == 1, na.rm = TRUE),
    perc_multiple_org_binary = n_multiple_org_binary / organic_vendors,
    median_multiple_org_count = median(multiple_org_count, na.rm = TRUE),
    iqr_multiple_org_count = IQR(multiple_org_count, na.rm = TRUE)
  ) %>%
  ungroup()

print(tab3_country_data)

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 3 - country")
writeData(table_outputs, sheet = "Table 3 - country", x = tab3_country_data)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)
```

##### Overall
```{r echo = FALSE, message = FALSE, warning = FALSE}
# N, %, median and IQR - overall
tab3_overall_data <- data_clean %>%
  summarize(
    organic_vendors = sum(org_vendor == 1, na.rm = TRUE),
    n_multiple_org_binary = sum(multiple_org_binary == 1, na.rm = TRUE),
    perc_multiple_org_binary = n_multiple_org_binary / organic_vendors,
    median_multiple_org_count = median(multiple_org_count, na.rm = TRUE),
    iqr_multiple_org_count = IQR(multiple_org_count, na.rm = TRUE)
  ) %>%
  ungroup()

print(tab3_overall_data)

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 3 - overall")
writeData(table_outputs, sheet = "Table 3 - overall", x = tab3_overall_data)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```


### Exploratory Analysis: Organic versus non-organic vendor characteristics

#### Table 4

##### Country-level

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Summarize the data grouped by `org_vendor` and `country`
tab4_country_data <- data_clean %>%
  group_by(country, org_vendor) %>%
  summarize(
    median_vendor_cashiers = median(vendor_cashiers, na.rm = TRUE),
    iqr_vendor_cashiers = IQR(vendor_cashiers, na.rm = TRUE),
    min_vendor_cashiers = min(vendor_cashiers, na.rm = TRUE),
    max_vendor_cashiers = max(vendor_cashiers, na.rm = TRUE),
    
    median_days_open_count = median(days_open_count, na.rm = TRUE),
    iqr_days_open_count = IQR(days_open_count, na.rm = TRUE),
    min_days_open_count = min(days_open_count, na.rm = TRUE),
    max_days_open_count = max(days_open_count, na.rm = TRUE),
    
    median_foods_count = median(foods_count, na.rm = TRUE),
    iqr_foods_count = IQR(foods_count, na.rm = TRUE),
    min_foods_count = min(foods_count, na.rm = TRUE),
    max_foods_count = max(foods_count, na.rm = TRUE)
  ) %>%
  ungroup()

# Display the country-level results
print(tab4_country_data)

# Relabel organic vendor status
tab4_country_data <- tab4_country_data %>%
  mutate(org_vendor = recode(org_vendor, '1' = 'Organic','0' = 'Non-organic'))

# Create the gt table
tab4_country <- tab4_country_data %>%
  gt(rowname_col = "org_vendor", groupname_col = c("country")) %>%
  cols_label(
    country = "Country",
    org_vendor = "Organic status",
    
    median_vendor_cashiers = "Cashiers, median(IQR), min-max",
    iqr_vendor_cashiers = " ",
    min_vendor_cashiers = " ",
    max_vendor_cashiers = " ",
    
    median_days_open_count = "Days open, median(IQR), min-max",
    iqr_days_open_count = " ",
    min_days_open_count = " ",
    max_days_open_count = " ",
    
    median_foods_count = "Sentinel products sold, median(IQR), min-max",
    iqr_foods_count = " ",
    min_foods_count = " ",
    max_foods_count = " "
  ) %>%
  cols_merge(
    columns = c("median_vendor_cashiers", "iqr_vendor_cashiers", 
                "min_vendor_cashiers", "max_vendor_cashiers"),
    pattern = "{1}({2}), {3}-{4}"
  ) %>%
    cols_merge(
    columns = c("median_days_open_count", "iqr_days_open_count", 
                "min_days_open_count", "max_days_open_count"),
    pattern = "{1}({2}), {3}-{4}"
  ) %>%
    cols_merge(
    columns = c("median_foods_count", "iqr_foods_count", 
                "min_foods_count", "max_foods_count"),
    pattern = "{1}({2}), {3}-{4}"
  ) %>%
  sub_missing() 

#print(tab4_country)

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 4 - country")
writeData(table_outputs, sheet = "Table 4 - country", x = tab4_country)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```

##### Overall

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Summarize the data for overall statistics grouped by `org_vendor`
tab4_overall_data <- data_clean %>%
  group_by(org_vendor) %>%
  summarize(
    median_vendor_cashiers = median(vendor_cashiers, na.rm = TRUE),
    iqr_vendor_cashiers = IQR(vendor_cashiers, na.rm = TRUE),
    min_vendor_cashiers = min(vendor_cashiers, na.rm = TRUE),
    max_vendor_cashiers = max(vendor_cashiers, na.rm = TRUE),
    
    median_days_open_count = median(days_open_count, na.rm = TRUE),
    iqr_days_open_count = IQR(days_open_count, na.rm = TRUE),
    min_days_open_count = min(days_open_count, na.rm = TRUE),
    max_days_open_count = max(days_open_count, na.rm = TRUE),
    
    median_foods_count = median(foods_count, na.rm = TRUE),
    iqr_foods_count = IQR(foods_count, na.rm = TRUE),
    min_foods_count = min(foods_count, na.rm = TRUE),
    max_foods_count = max(foods_count, na.rm = TRUE)
  ) %>%
  ungroup()

# Display the overall results
print(tab4_overall_data)

# Relabel organic vendor status
tab4_overall_data <- tab4_overall_data %>%
  mutate(org_vendor = recode(org_vendor, '1' = 'Organic','0' = 'Non-organic'))


# Create the gt table
tab4_overall <- tab4_overall_data %>%
  gt() %>%
  cols_label(
    org_vendor = "Organic status",
    
    median_vendor_cashiers = "Cashiers, median(IQR), min-max",
    iqr_vendor_cashiers = " ",
    min_vendor_cashiers = " ",
    max_vendor_cashiers = " ",
    
    median_days_open_count = "Days open, median(IQR), min-max",
    iqr_days_open_count = " ",
    min_days_open_count = " ",
    max_days_open_count = " ",
    
    median_foods_count = "Sentinel products sold, median(IQR), min-max",
    iqr_foods_count = " ",
    min_foods_count = " ",
    max_foods_count = " "
  ) %>%
  cols_merge(
    columns = c("median_vendor_cashiers", "iqr_vendor_cashiers", 
                "min_vendor_cashiers", "max_vendor_cashiers"),
    pattern = "{1}({2}), {3}-{4}"
  ) %>%
    cols_merge(
    columns = c("median_days_open_count", "iqr_days_open_count", 
                "min_days_open_count", "max_days_open_count"),
    pattern = "{1}({2}), {3}-{4}"
  ) %>%
    cols_merge(
    columns = c("median_foods_count", "iqr_foods_count", 
                "min_foods_count", "max_foods_count"),
    pattern = "{1}({2}), {3}-{4}"
  ) %>%
  sub_missing() 

#print(tab4_overall)


# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 4 - overall")
writeData(table_outputs, sheet = "Table 4 - overall", x = tab4_overall)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)
```


## 2. How affordable is a sentinel organic food (rice) compared to a non-organic sentinel food (rice) in urban food environments? How does this vary across different geographic contexts?

### Hypothesis 2a. The price of organic rice will be significantly higher than the price of non-organic rice overall and at the country level.


```{r include=FALSE}

# Load cleaned rice prices data
rice_prices_data <- read.xlsx("rice_prices_data_clean.xlsx", sheet = "data")

```

#### Wilcoxon Rank-Sum Test / Mann-Whitney U test

##### Overall results
```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame of overall prices
mw_rice_prices_data_overall <- rice_prices_data %>%
  select(rice_price_org_kg_usd, rice_price_conv_kg_usd)

# Reshape data to long form
reshaped_data <- mw_rice_prices_data_overall %>%
  pivot_longer(cols = c(rice_price_org_kg_usd, rice_price_conv_kg_usd), 
               names_to = "type", 
               values_to = "price") %>%
  mutate(type = ifelse(type == "rice_price_org_kg_usd", "organic", "conventional")) %>%
  filter(!is.na(price))

# Specify order because function otherwise sets first group alphabetically
reshaped_data$type <- factor(reshaped_data$type, 
                              levels = c("organic", "conventional"))

# Overall Mann-Whitney U test
overall_test <- wilcox.test(price ~ type, data = reshaped_data, 
                            alternative = "greater")

overall_p_value_one_tailed <- overall_test$p.value / 2

print(overall_test)
cat("Overall Mann-Whitney U test p-value (one-tailed):", overall_p_value_one_tailed, "\n")

```

##### Country-level results: Brazil
```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame of Brazil prices
mw_rice_prices_data_brazil <- rice_prices_data %>%
  select(country, rice_price_org_kg_usd, rice_price_conv_kg_usd) %>%
  filter(country == "Brazil")
  
# Reshape data to long form
reshaped_data_brazil <- mw_rice_prices_data_brazil %>%
  pivot_longer(cols = c(rice_price_org_kg_usd, rice_price_conv_kg_usd), 
               names_to = "type", 
               values_to = "price") %>%
  mutate(type = ifelse(type == "rice_price_org_kg_usd", "organic", "conventional")) %>%
  filter(!is.na(price))

# Specify order because function otherwise sets first group alphabetically
reshaped_data_brazil$type <- factor(reshaped_data_brazil$type, 
                              levels = c("organic", "conventional"))

# Brazil Mann-Whitney U test
brazil_test <- wilcox.test(price ~ type, data = reshaped_data_brazil, 
                            alternative = "greater")

brazil_p_value_one_tailed <- brazil_test$p.value / 2

print(brazil_test)
cat("Overall Mann-Whitney U test p-value (one-tailed):", brazil_p_value_one_tailed, "\n")

```


##### Country-level results: India
```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame of India prices
mw_rice_prices_data_india <- rice_prices_data %>%
  select(country, rice_price_org_kg_usd, rice_price_conv_kg_usd) %>%
  filter(country == "India")
  
# Reshape data to long form
reshaped_data_india <- mw_rice_prices_data_india %>%
  pivot_longer(cols = c(rice_price_org_kg_usd, rice_price_conv_kg_usd), 
               names_to = "type", 
               values_to = "price") %>%
  mutate(type = ifelse(type == "rice_price_org_kg_usd", "organic", "conventional")) %>%
  filter(!is.na(price))

# Specify order because function otherwise sets first group alphabetically
reshaped_data_india$type <- factor(reshaped_data_india$type, 
                              levels = c("organic", "conventional"))

# India Mann-Whitney U test
india_test <- wilcox.test(price ~ type, data = reshaped_data_india, 
                            alternative = "greater")

india_p_value_one_tailed <- india_test$p.value / 2

print(india_test)
cat("Overall Mann-Whitney U test p-value (one-tailed):", india_p_value_one_tailed, "\n")

```

##### Country-level results: UK
```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame of UK prices
mw_rice_prices_data_uk <- rice_prices_data %>%
  select(country, rice_price_org_kg_usd, rice_price_conv_kg_usd) %>%
  filter(country == "UK")
  
# Reshape data to long form
reshaped_data_uk <- mw_rice_prices_data_uk %>%
  pivot_longer(cols = c(rice_price_org_kg_usd, rice_price_conv_kg_usd), 
               names_to = "type", 
               values_to = "price") %>%
  mutate(type = ifelse(type == "rice_price_org_kg_usd", "organic", "conventional")) %>%
  filter(!is.na(price))

# Specify order because function otherwise sets first group alphabetically
reshaped_data_uk$type <- factor(reshaped_data_uk$type, 
                              levels = c("organic", "conventional"))

# UK Mann-Whitney U test
uk_test <- wilcox.test(price ~ type, data = reshaped_data_uk, 
                            alternative = "greater")

uk_p_value_one_tailed <- uk_test$p.value / 2

print(uk_test)
cat("Overall Mann-Whitney U test p-value (one-tailed):", uk_p_value_one_tailed, "\n")

```



#### Table 5

##### City-level

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Calculate number of organic and conventional vendors, median, IQR, min and max price
tab5_city_data <- rice_prices_data %>%
  group_by(country, city) %>%
  summarise(
    count_org_rice_vendors = sum(!is.na(rice_price_org_kg_usd)),
    count_conv_rice_vendors = sum(!is.na(rice_price_conv_kg_usd)),
    median_org_rice = median(rice_price_org_kg_usd, na.rm = TRUE),
    iqr_org_rice = IQR(rice_price_org_kg_usd, na.rm = TRUE),
    min_org_rice = min(rice_price_org_kg_usd, na.rm = TRUE),
    max_org_rice = max(rice_price_org_kg_usd, na.rm = TRUE),
    median_conv_rice = median(rice_price_conv_kg_usd, na.rm = TRUE),
    iqr_conv_rice = IQR(rice_price_conv_kg_usd, na.rm = TRUE),
    min_conv_rice = min(rice_price_conv_kg_usd, na.rm = TRUE),
    max_conv_rice = max(rice_price_conv_kg_usd, na.rm = TRUE),
  ) %>%
  ungroup()

# Create the gt table
tab5_city <- tab5_city_data %>%
  gt(rowname_col = "city", groupname_col = c("country")) %>%
  cols_label(
    country = "Country",
    city = "City",
    count_org_rice_vendors = "Organic sample size (n)",
    count_conv_rice_vendors = "Conventional sample size (n)",
    median_org_rice = "Organic median (IQR), min-max (US$)",
    iqr_org_rice = " ",
    min_org_rice = " ",
    max_org_rice = " ",
    median_conv_rice = "Conventional median (IQR), min-max (US$)",
    iqr_conv_rice = " ",
    min_conv_rice = " ",
    max_conv_rice = " "
  ) %>%
  cols_merge(
    columns = c("median_org_rice", "iqr_org_rice", "min_org_rice", "max_org_rice"),
    pattern = "{1} ({2}), {3}-{4}"
  ) %>%
    cols_merge(
    columns = c("median_conv_rice", "iqr_conv_rice", "min_conv_rice", "max_conv_rice"),
    pattern = "{1} ({2}), {3}-{4}"
  ) %>%
  fmt_number(
    columns = vars(median_org_rice, iqr_org_rice, min_org_rice, max_org_rice,
                   median_conv_rice, iqr_conv_rice, min_conv_rice, max_conv_rice),
    decimals = 2
  ) %>%
  summary_rows(
    groups = everything(),
    columns = vars(count_org_rice_vendors,count_conv_rice_vendors),
    fns = list(total = ~sum(., na.rm = TRUE)),
    formatter = fmt_number,
    decimals = 0,
  ) %>%
  sub_missing() 
  
# Display the table
tab5_city

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 5 - city")
writeData(table_outputs, sheet = "Table 5 - city", x = tab5_city)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```

##### Country-level


```{r echo = FALSE, message = FALSE, warning = FALSE}

# Calculate number of organic and conventional vendors, median, IQR, min and max price
tab5_country_data <- rice_prices_data %>%
  group_by(country) %>%
  summarise(
    count_org_rice_vendors = sum(!is.na(rice_price_org_kg_usd)),
    count_conv_rice_vendors = sum(!is.na(rice_price_conv_kg_usd)),
    median_org_rice = median(rice_price_org_kg_usd, na.rm = TRUE),
    iqr_org_rice = IQR(rice_price_org_kg_usd, na.rm = TRUE),
    min_org_rice = min(rice_price_org_kg_usd, na.rm = TRUE),
    max_org_rice = max(rice_price_org_kg_usd, na.rm = TRUE),
    median_conv_rice = median(rice_price_conv_kg_usd, na.rm = TRUE),
    iqr_conv_rice = IQR(rice_price_conv_kg_usd, na.rm = TRUE),
    min_conv_rice = min(rice_price_conv_kg_usd, na.rm = TRUE),
    max_conv_rice = max(rice_price_conv_kg_usd, na.rm = TRUE),
  ) %>%
  ungroup()

tab5_country <- tab5_country_data %>%
  gt() %>%
  cols_label(
    country = "Country",
    count_org_rice_vendors = "Organic sample size (n)",
    count_conv_rice_vendors = "Conventional sample size (n)",
    median_org_rice = "Organic median (IQR), min-max (US$)",
    iqr_org_rice = " ",
    min_org_rice = " ",
    max_org_rice = " ",
    median_conv_rice = "Conventional median (IQR), min-max (US$)",
    iqr_conv_rice = " ",
    min_conv_rice = " ",
    max_conv_rice = " "
  ) %>%
  cols_merge(
    columns = c("median_org_rice", "iqr_org_rice", "min_org_rice", "max_org_rice"),
    pattern = "{1} ({2}), {3}-{4}"
  ) %>%
    cols_merge(
    columns = c("median_conv_rice", "iqr_conv_rice", "min_conv_rice", "max_conv_rice"),
    pattern = "{1} ({2}), {3}-{4}"
  ) %>%
  fmt_number(
    columns = vars(median_org_rice, iqr_org_rice, min_org_rice, max_org_rice,
                   median_conv_rice, iqr_conv_rice, min_conv_rice, max_conv_rice),
    decimals = 2
  ) %>%
  grand_summary_rows(
    columns = vars(count_org_rice_vendors,count_conv_rice_vendors),
    fns = list(total = ~sum(., na.rm = TRUE)),
    formatter = fmt_number,
    decimals = 0,
  ) %>%
  sub_missing() 

# Display the table
tab5_country

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 5 - country")
writeData(table_outputs, sheet = "Table 5 - country", x = tab5_country)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```

##### Overall


```{r echo = FALSE, message = FALSE, warning = FALSE}

# Calculate number of organic and conventional vendors, median, IQR, min and max price
tab5_overall_data <- rice_prices_data %>%
  summarise(
    count_org_rice_vendors = sum(!is.na(rice_price_org_kg_usd)),
    count_conv_rice_vendors = sum(!is.na(rice_price_conv_kg_usd)),
    median_org_rice = median(rice_price_org_kg_usd, na.rm = TRUE),
    iqr_org_rice = IQR(rice_price_org_kg_usd, na.rm = TRUE),
    min_org_rice = min(rice_price_org_kg_usd, na.rm = TRUE),
    max_org_rice = max(rice_price_org_kg_usd, na.rm = TRUE),
    median_conv_rice = median(rice_price_conv_kg_usd, na.rm = TRUE),
    iqr_conv_rice = IQR(rice_price_conv_kg_usd, na.rm = TRUE),
    min_conv_rice = min(rice_price_conv_kg_usd, na.rm = TRUE),
    max_conv_rice = max(rice_price_conv_kg_usd, na.rm = TRUE),
  ) %>%
  ungroup()

# Create gt table
tab5_overall <- tab5_overall_data %>%
  gt() %>%
  cols_label(
    count_org_rice_vendors = "Organic sample size (n)",
    count_conv_rice_vendors = "Conventional sample size (n)",
    median_org_rice = "Organic median (IQR), min-max (US$)",
    iqr_org_rice = " ",
    min_org_rice = " ",
    max_org_rice = " ",
    median_conv_rice = "Conventional median (IQR), min-max (US$)",
    iqr_conv_rice = " ",
    min_conv_rice = " ",
    max_conv_rice = " "
  ) %>%
  cols_merge(
    columns = c("median_org_rice", "iqr_org_rice", "min_org_rice", "max_org_rice"),
    pattern = "{1} ({2}), {3}-{4}"
  ) %>%
    cols_merge(
    columns = c("median_conv_rice", "iqr_conv_rice", "min_conv_rice", "max_conv_rice"),
    pattern = "{1} ({2}), {3}-{4}"
  ) %>%
  fmt_number(
    columns = vars(median_org_rice, iqr_org_rice, min_org_rice, max_org_rice,
                   median_conv_rice, iqr_conv_rice, min_conv_rice, max_conv_rice),
    decimals = 2
  ) %>%
  sub_missing() 

# Display the table
tab5_overall

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 5 - overall")
writeData(table_outputs, sheet = "Table 5 - overall", x = tab5_overall)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```

### Hypothesis 2b. The price of organic rice will be significantly higher than the price of non-organic rice when sold at the same vendor location.

#### Wilcoxon Signed Rank Test

##### Overall results
```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame of rice prices for vendors selling both organic and conventional
wsr_rice_prices_data_overall <- rice_prices_data %>%
  select(rice_price_org_kg_usd, rice_price_conv_kg_usd, rice_price_both) %>%
  filter(rice_price_both == 1)

# Overall Wilcoxon Signed Rank test
wsr_overall_test <- wilcox.test(wsr_rice_prices_data_overall$rice_price_org_kg_usd,
                            wsr_rice_prices_data_overall$rice_price_conv_kg_usd,
                            alternative = "greater", paired = TRUE)

wsr_overall_p_value_one_tailed <- wsr_overall_test$p.value / 2

print(wsr_overall_test)
cat("Overall Wilcoxon Signed Rank test p-value (one-tailed):", wsr_overall_p_value_one_tailed, "\n")

```

##### Country-level results: Brazil
```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame of rice prices for vendors selling both organic and conventional
wsr_rice_prices_data_brazil <- rice_prices_data %>%
  select(country, rice_price_org_kg_usd, rice_price_conv_kg_usd, rice_price_both) %>%
  filter(rice_price_both == 1) %>%
  filter(country == "Brazil")

# Overall Wilcoxon Signed Rank test
wsr_brazil_test <- wilcox.test(wsr_rice_prices_data_brazil$rice_price_org_kg_usd,
                            wsr_rice_prices_data_brazil$rice_price_conv_kg_usd,
                            alternative = "greater", paired = TRUE)

wsr_brazil_p_value_one_tailed <- wsr_brazil_test$p.value / 2

print(wsr_brazil_test)
cat("Overall Wilcoxon Signed Rank test p-value (one-tailed):", wsr_brazil_p_value_one_tailed, "\n")

```


##### Country-level results: India
```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame of rice prices for vendors selling both organic and conventional
wsr_rice_prices_data_india <- rice_prices_data %>%
  select(country, rice_price_org_kg_usd, rice_price_conv_kg_usd, rice_price_both) %>%
  filter(rice_price_both == 1) %>%
  filter(country == "India")

# Overall Wilcoxon Signed Rank test
wsr_india_test <- wilcox.test(wsr_rice_prices_data_india$rice_price_org_kg_usd,
                            wsr_rice_prices_data_india$rice_price_conv_kg_usd,
                            alternative = "greater", paired = TRUE)

wsr_india_p_value_one_tailed <- wsr_india_test$p.value / 2

print(wsr_india_test)
cat("Overall Wilcoxon Signed Rank test p-value (one-tailed):", wsr_india_p_value_one_tailed, "\n")
```

##### Country-level results: UK
```{r echo = FALSE, message = FALSE, warning = FALSE}

# Create data frame of rice prices for vendors selling both organic and conventional
wsr_rice_prices_data_uk <- rice_prices_data %>%
  select(country, rice_price_org_kg_usd, rice_price_conv_kg_usd, rice_price_both) %>%
  filter(rice_price_both == 1) %>%
  filter(country == "UK")

# Overall Wilcoxon Signed Rank test
wsr_uk_test <- wilcox.test(wsr_rice_prices_data_uk$rice_price_org_kg_usd,
                            wsr_rice_prices_data_uk$rice_price_conv_kg_usd,
                            alternative = "greater", paired = TRUE)

wsr_uk_p_value_one_tailed <- wsr_uk_test$p.value / 2

print(wsr_uk_test)
cat("Overall Wilcoxon Signed Rank test p-value (one-tailed):", wsr_uk_p_value_one_tailed, "\n")
```


#### Table S1

##### City-level

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Calculate number of organic and conventional vendors, median, IQR, min and max price
# Filtered on vendors with both organic and conventional rice
tabs1_city_data <- rice_prices_data %>%
  filter(rice_price_both == 1) %>%
  group_by(country, city) %>%
  summarise(
    count_org_rice_vendors = sum(!is.na(rice_price_org_kg_usd)),
    count_conv_rice_vendors = sum(!is.na(rice_price_conv_kg_usd)),
    median_org_rice = median(rice_price_org_kg_usd, na.rm = TRUE),
    iqr_org_rice = IQR(rice_price_org_kg_usd, na.rm = TRUE),
    min_org_rice = min(rice_price_org_kg_usd, na.rm = TRUE),
    max_org_rice = max(rice_price_org_kg_usd, na.rm = TRUE),
    median_conv_rice = median(rice_price_conv_kg_usd, na.rm = TRUE),
    iqr_conv_rice = IQR(rice_price_conv_kg_usd, na.rm = TRUE),
    min_conv_rice = min(rice_price_conv_kg_usd, na.rm = TRUE),
    max_conv_rice = max(rice_price_conv_kg_usd, na.rm = TRUE),
  ) %>%
  ungroup()

# Create the gt table
tabs1_city <- tabs1_city_data %>%
  gt(rowname_col = "city", groupname_col = c("country")) %>%
  cols_label(
    country = "Country",
    city = "City",
    count_org_rice_vendors = "Organic sample size (n)",
    count_conv_rice_vendors = "Conventional sample size (n)",
    median_org_rice = "Organic median (IQR), min-max (US$)",
    iqr_org_rice = " ",
    min_org_rice = " ",
    max_org_rice = " ",
    median_conv_rice = "Conventional median (IQR), min-max (US$)",
    iqr_conv_rice = " ",
    min_conv_rice = " ",
    max_conv_rice = " "
  ) %>%
  cols_merge(
    columns = c("median_org_rice", "iqr_org_rice", "min_org_rice", "max_org_rice"),
    pattern = "{1} ({2}), {3}-{4}"
  ) %>%
    cols_merge(
    columns = c("median_conv_rice", "iqr_conv_rice", "min_conv_rice", "max_conv_rice"),
    pattern = "{1} ({2}), {3}-{4}"
  ) %>%
  fmt_number(
    columns = vars(median_org_rice, iqr_org_rice, min_org_rice, max_org_rice,
                   median_conv_rice, iqr_conv_rice, min_conv_rice, max_conv_rice),
    decimals = 2
  ) %>%
  summary_rows(
    groups = everything(),
    columns = vars(count_org_rice_vendors,count_conv_rice_vendors),
    fns = list(total = ~sum(., na.rm = TRUE)),
    formatter = fmt_number,
    decimals = 0,
  ) %>%
  sub_missing() 
  
# Display the table
tabs1_city

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table S1 - city")
writeData(table_outputs, sheet = "Table S1 - city", x = tabs1_city)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```

##### Country-level

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Calculate number of organic and conventional vendors, median, IQR, min and max price
# Filtered on vendors with both organic and conventional rice
tabs1_country_data <- rice_prices_data %>%
  filter(rice_price_both == 1) %>%
  group_by(country) %>%
  summarise(
    count_org_rice_vendors = sum(!is.na(rice_price_org_kg_usd)),
    count_conv_rice_vendors = sum(!is.na(rice_price_conv_kg_usd)),
    median_org_rice = median(rice_price_org_kg_usd, na.rm = TRUE),
    iqr_org_rice = IQR(rice_price_org_kg_usd, na.rm = TRUE),
    min_org_rice = min(rice_price_org_kg_usd, na.rm = TRUE),
    max_org_rice = max(rice_price_org_kg_usd, na.rm = TRUE),
    median_conv_rice = median(rice_price_conv_kg_usd, na.rm = TRUE),
    iqr_conv_rice = IQR(rice_price_conv_kg_usd, na.rm = TRUE),
    min_conv_rice = min(rice_price_conv_kg_usd, na.rm = TRUE),
    max_conv_rice = max(rice_price_conv_kg_usd, na.rm = TRUE),
  ) %>%
  ungroup()

tabs1_country <- tabs1_country_data %>%
  gt() %>%
  cols_label(
    country = "Country",
    count_org_rice_vendors = "Organic sample size (n)",
    count_conv_rice_vendors = "Conventional sample size (n)",
    median_org_rice = "Organic median (IQR), min-max (US$)",
    iqr_org_rice = " ",
    min_org_rice = " ",
    max_org_rice = " ",
    median_conv_rice = "Conventional median (IQR), min-max (US$)",
    iqr_conv_rice = " ",
    min_conv_rice = " ",
    max_conv_rice = " "
  ) %>%
  cols_merge(
    columns = c("median_org_rice", "iqr_org_rice", "min_org_rice", "max_org_rice"),
    pattern = "{1} ({2}), {3}-{4}"
  ) %>%
    cols_merge(
    columns = c("median_conv_rice", "iqr_conv_rice", "min_conv_rice", "max_conv_rice"),
    pattern = "{1} ({2}), {3}-{4}"
  ) %>%
  fmt_number(
    columns = vars(median_org_rice, iqr_org_rice, min_org_rice, max_org_rice,
                   median_conv_rice, iqr_conv_rice, min_conv_rice, max_conv_rice),
    decimals = 2
  ) %>%
  grand_summary_rows(
    columns = vars(count_org_rice_vendors,count_conv_rice_vendors),
    fns = list(total = ~sum(., na.rm = TRUE)),
    formatter = fmt_number,
    decimals = 0,
  ) %>%
  sub_missing() 

# Display the table
tabs1_country

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table S1 - country")
writeData(table_outputs, sheet = "Table S1 - country", x = tabs1_country)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)


```


##### Overall

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Calculate number of organic and conventional vendors, median, IQR, min and max price
# Filtered on vendors with both organic and conventional rice
tabs1_overall_data <- rice_prices_data %>%
  filter(rice_price_both == 1) %>%
  summarise(
    count_org_rice_vendors = sum(!is.na(rice_price_org_kg_usd)),
    count_conv_rice_vendors = sum(!is.na(rice_price_conv_kg_usd)),
    median_org_rice = median(rice_price_org_kg_usd, na.rm = TRUE),
    iqr_org_rice = IQR(rice_price_org_kg_usd, na.rm = TRUE),
    min_org_rice = min(rice_price_org_kg_usd, na.rm = TRUE),
    max_org_rice = max(rice_price_org_kg_usd, na.rm = TRUE),
    median_conv_rice = median(rice_price_conv_kg_usd, na.rm = TRUE),
    iqr_conv_rice = IQR(rice_price_conv_kg_usd, na.rm = TRUE),
    min_conv_rice = min(rice_price_conv_kg_usd, na.rm = TRUE),
    max_conv_rice = max(rice_price_conv_kg_usd, na.rm = TRUE),
  ) %>%
  ungroup()

tabs1_overall <- tabs1_overall_data %>%
  gt() %>%
  cols_label(
    count_org_rice_vendors = "Organic sample size (n)",
    count_conv_rice_vendors = "Conventional sample size (n)",
    median_org_rice = "Organic median (IQR), min-max (US$)",
    iqr_org_rice = " ",
    min_org_rice = " ",
    max_org_rice = " ",
    median_conv_rice = "Conventional median (IQR), min-max (US$)",
    iqr_conv_rice = " ",
    min_conv_rice = " ",
    max_conv_rice = " "
  ) %>%
  cols_merge(
    columns = c("median_org_rice", "iqr_org_rice", "min_org_rice", "max_org_rice"),
    pattern = "{1} ({2}), {3}-{4}"
  ) %>%
    cols_merge(
    columns = c("median_conv_rice", "iqr_conv_rice", "min_conv_rice", "max_conv_rice"),
    pattern = "{1} ({2}), {3}-{4}"
  ) %>%
  fmt_number(
    columns = vars(median_org_rice, iqr_org_rice, min_org_rice, max_org_rice,
                   median_conv_rice, iqr_conv_rice, min_conv_rice, max_conv_rice),
    decimals = 2
  ) %>%
  sub_missing() 

# Display the table
tabs1_overall

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table S1 - overall")
writeData(table_outputs, sheet = "Table S1 - overall", x = tabs1_overall)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)


```

## 3. What are the marketing characteristics of organic food in urban food environments? How does this vary across different geographic and socioeconomic contexts? 

### Terminologies - Table 6

##### Overall

```{r echo = FALSE, message = FALSE, warning = FALSE}

# Note: If I want to summarise just the number of vendors using the term,
# the code for summing should be >0

# Create new instance of dataset for Table 6
tab6_data <- data_clean


## OVERALL----

# PRODUCT-LEVEL SUMMARY

# Vector of product abbreviations
products <- c("tom", "leaf", "ban", "man", "fj", "milk", "cof", "tea", "mill", "chic", "daal", "wht", "rice", "nut")

# Define a function to summarize data for a given product and dataset
tab6_product_fn <- function(product) {
  tab6_data %>%
    summarise(
      org_count = sum(get(paste0(product, "_org")) == "Yes", na.rm = TRUE),
      term_organic_count = sum(get(paste0(product, "_org_terms_Organic")) == 1, na.rm = TRUE),
      term_organic_perc = term_organic_count / org_count,
      term_natural_count = sum(get(paste0(product, "_org_terms_Natural")) == 1, na.rm = TRUE),
      term_natural_perc = term_natural_count / org_count,
      term_chemfree_count = sum(get(paste0(product, "_org_terms_Chemical-free")) == 1, na.rm = TRUE),
      term_chemfree_perc = term_chemfree_count / org_count,
      term_pestfree_count = sum(get(paste0(product, "_org_terms_Pesticide-free")) == 1, na.rm = TRUE),
      term_pestfree_perc = term_pestfree_count / org_count,
      term_bioprod_count = sum(get(paste0(product, "_org_terms_Bioproducts")) == 1, na.rm = TRUE),
      term_bioprod_perc = term_bioprod_count / org_count,
      term_bio_count = sum(get(paste0(product, "_org_terms_Bio")) == 1, na.rm = TRUE),
      term_bio_perc = term_bio_count / org_count,
      term_eco_count = sum(get(paste0(product, "_org_terms_Eco")) == 1, na.rm = TRUE),
      term_eco_perc = term_eco_count / org_count,
      term_gmo_count = sum(get(paste0(product, "_org_terms_GMO-free")) == 1, na.rm = TRUE),
      term_gmo_perc = term_gmo_count / org_count,
      #term_dontknow_count = sum(get(paste0(product, "_org_terms_Don't know")) == 1, na.rm = TRUE),
      #term_dontknow_perc = term_dontknow_count / org_count
    ) %>%
    mutate(
      product = product,
      category = case_when(product %in% c("fj", "milk", "cof", "tea") ~ "beverages",
                           product %in% c("tom", "leaf", "ban", "man") ~ "fresh produce",
                           TRUE ~ "other")
      ) %>% 
    select(category, product, everything())
}

# Apply the function to each product and combine the results
product_summary_list <- lapply(products, tab6_product_fn)
tab6_product_summary <- bind_rows(product_summary_list)

## CATEGORY-LEVEL SUMMARY

tab6_category_summary <- tab6_product_summary %>%
  group_by(category) %>%
  summarise(
    org_count = sum(org_count, na.rm = TRUE),
    term_organic_count = sum(term_organic_count, na.rm = TRUE),
    term_organic_perc = mean(term_organic_perc, na.rm = TRUE),
    term_natural_count = sum(term_natural_count, na.rm = TRUE),
    term_natural_perc = mean(term_natural_perc, na.rm = TRUE),
    term_chemfree_count = sum(term_chemfree_count, na.rm = TRUE),
    term_chemfree_perc = mean(term_chemfree_perc, na.rm = TRUE),
    term_pestfree_count = sum(term_pestfree_count, na.rm = TRUE),
    term_pestfree_perc = mean(term_pestfree_perc, na.rm = TRUE),
    term_bioprod_count = sum(term_bioprod_count, na.rm = TRUE),
    term_bioprod_perc = mean(term_bioprod_perc, na.rm = TRUE),
    term_bio_count = sum(term_bio_count, na.rm = TRUE),
    term_bio_perc = mean(term_bio_perc, na.rm = TRUE),
    term_eco_count = sum(term_eco_count, na.rm = TRUE),
    term_eco_perc = mean(term_eco_perc, na.rm = TRUE),
    term_gmo_count = sum(term_gmo_count, na.rm = TRUE),
    term_gmo_perc = mean(term_gmo_perc, na.rm = TRUE),
    #term_dontknow_count = sum(term_dontknow_count, na.rm = TRUE),
    #term_dontknow_perc = mean(term_dontknow_perc, na.rm = TRUE)
  )


# Create gt table
tab6_categories_overall <- tab6_category_summary %>%
  gt() %>%
  cols_label(
    category = "Category",
    org_count = "Total organic products",
    term_organic_count = "Organic, n(%)",
    term_organic_perc = " ",
    term_natural_count = "Natural, n(%)",
    term_natural_perc = " ",
    term_chemfree_count = "Chemical-free, n(%)",
    term_chemfree_perc = " ",
    term_pestfree_count = "Pesticide-free, n(%)",
    term_pestfree_perc = " ",
    term_bioprod_count = "Bioproduct, n(%)",
    term_bioprod_perc = " ",
    term_bio_count = "Bio, n(%)",
    term_bio_perc = " ",
    term_eco_count = "Eco, n(%)",
    term_eco_perc = " ",
    term_gmo_count = "GMO-free, n(%)",
    term_gmo_perc = " ",
    #term_dontknow_count = "Don't know, n(%)",
    #term_dontknow_perc = " ",
  ) %>%
  cols_merge(
    columns = c("term_organic_count", "term_organic_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_natural_count", "term_natural_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_chemfree_count", "term_chemfree_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_pestfree_count", "term_pestfree_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_bioprod_count", "term_bioprod_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_bio_count", "term_bio_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_eco_count", "term_eco_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_gmo_count", "term_gmo_perc"),
    pattern = "{1} ({2})"
  ) %>%
  #cols_merge(
  #  columns = c("term_dontknow_count", "term_dontknow_perc"),
  #  pattern = "{1} ({2})"
  #) %>%
  fmt_percent(
    columns = c(term_organic_perc, term_natural_perc, term_chemfree_perc,
                   term_pestfree_perc, term_bioprod_perc, term_bio_perc,
                   term_eco_perc, term_gmo_perc),
    decimals = 0
  ) %>%
  tab_header(
    title = "Table 6 - Overall"
  ) %>%
  grand_summary_rows(
    columns = c(org_count, term_organic_count, term_natural_count, term_chemfree_count,
                   term_pestfree_count, term_bioprod_count, term_bio_count,
                   term_eco_count, term_gmo_count),
    fns = list(total = ~sum(., na.rm = TRUE)),
    formatter = fmt_number,
    decimals = 0,
  ) %>%
  sub_missing() 

# Display the table
tab6_categories_overall

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 6 - overall")
writeData(table_outputs, sheet = "Table 6 - overall", x = tab6_categories_overall)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```


##### Brazil

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Create new instance of dataset for Table 6 - Brazil
tab6_data_brazil <- tab6_data %>%
  filter(country == "Brazil")

# PRODUCT-LEVEL SUMMARY

# Vector of product abbreviations
products <- c("tom", "leaf", "ban", "man", "fj", "milk", "cof", "tea", "mill", "chic", "daal", "wht", "rice", "nut")

# Define a function to summarize data for a given product and dataset
tab6_product_fn_brazil <- function(product) {
  tab6_data_brazil %>%
    summarise(
      org_count = sum(get(paste0(product, "_org")) == "Yes", na.rm = TRUE),
      term_organic_count = sum(get(paste0(product, "_org_terms_Organic")) == 1, na.rm = TRUE),
      term_organic_perc = term_organic_count / org_count,
      term_natural_count = sum(get(paste0(product, "_org_terms_Natural")) == 1, na.rm = TRUE),
      term_natural_perc = term_natural_count / org_count,
      term_chemfree_count = sum(get(paste0(product, "_org_terms_Chemical-free")) == 1, na.rm = TRUE),
      term_chemfree_perc = term_chemfree_count / org_count,
      term_pestfree_count = sum(get(paste0(product, "_org_terms_Pesticide-free")) == 1, na.rm = TRUE),
      term_pestfree_perc = term_pestfree_count / org_count,
      term_bioprod_count = sum(get(paste0(product, "_org_terms_Bioproducts")) == 1, na.rm = TRUE),
      term_bioprod_perc = term_bioprod_count / org_count,
      term_bio_count = sum(get(paste0(product, "_org_terms_Bio")) == 1, na.rm = TRUE),
      term_bio_perc = term_bio_count / org_count,
      term_eco_count = sum(get(paste0(product, "_org_terms_Eco")) == 1, na.rm = TRUE),
      term_eco_perc = term_eco_count / org_count,
      term_gmo_count = sum(get(paste0(product, "_org_terms_GMO-free")) == 1, na.rm = TRUE),
      term_gmo_perc = term_gmo_count / org_count,
      #term_dontknow_count = sum(get(paste0(product, "_org_terms_Don't know")) == 1, na.rm = TRUE),
      #term_dontknow_perc = term_dontknow_count / org_count
    ) %>%
    mutate(
      product = product,
      category = case_when(product %in% c("fj", "milk", "cof", "tea") ~ "beverages",
                           product %in% c("tom", "leaf", "ban", "man") ~ "fresh produce",
                           TRUE ~ "other")
    ) %>% 
    select(category, product, everything())
}

# Apply the function to each product and combine the results
product_summary_list_brazil <- lapply(products, tab6_product_fn_brazil)
tab6_product_summary_brazil <- bind_rows(product_summary_list_brazil)

## CATEGORY-LEVEL SUMMARY

tab6_category_summary_brazil <- tab6_product_summary_brazil %>%
  group_by(category) %>%
  summarise(
    org_count = sum(org_count, na.rm = TRUE),
    term_organic_count = sum(term_organic_count, na.rm = TRUE),
    term_organic_perc = mean(term_organic_perc, na.rm = TRUE),
    term_natural_count = sum(term_natural_count, na.rm = TRUE),
    term_natural_perc = mean(term_natural_perc, na.rm = TRUE),
    term_chemfree_count = sum(term_chemfree_count, na.rm = TRUE),
    term_chemfree_perc = mean(term_chemfree_perc, na.rm = TRUE),
    term_pestfree_count = sum(term_pestfree_count, na.rm = TRUE),
    term_pestfree_perc = mean(term_pestfree_perc, na.rm = TRUE),
    term_bioprod_count = sum(term_bioprod_count, na.rm = TRUE),
    term_bioprod_perc = mean(term_bioprod_perc, na.rm = TRUE),
    term_bio_count = sum(term_bio_count, na.rm = TRUE),
    term_bio_perc = mean(term_bio_perc, na.rm = TRUE),
    term_eco_count = sum(term_eco_count, na.rm = TRUE),
    term_eco_perc = mean(term_eco_perc, na.rm = TRUE),
    term_gmo_count = sum(term_gmo_count, na.rm = TRUE),
    term_gmo_perc = mean(term_gmo_perc, na.rm = TRUE),
    #term_dontknow_count = sum(term_dontknow_count, na.rm = TRUE),
    #term_dontknow_perc = mean(term_dontknow_perc, na.rm = TRUE)
  )


# Create gt table
tab6_categories_brazil <- tab6_category_summary_brazil %>%
  gt() %>%
  cols_label(
    category = "Category",
    org_count = "Total organic products",
    term_organic_count = "Organic, n(%)",
    term_organic_perc = " ",
    term_natural_count = "Natural, n(%)",
    term_natural_perc = " ",
    term_chemfree_count = "Chemical-free, n(%)",
    term_chemfree_perc = " ",
    term_pestfree_count = "Pesticide-free, n(%)",
    term_pestfree_perc = " ",
    term_bioprod_count = "Bioproduct, n(%)",
    term_bioprod_perc = " ",
    term_bio_count = "Bio, n(%)",
    term_bio_perc = " ",
    term_eco_count = "Eco, n(%)",
    term_eco_perc = " ",
    term_gmo_count = "GMO-free, n(%)",
    term_gmo_perc = " ",
    #term_dontknow_count = "Don't know, n(%)",
    #term_dontknow_perc = " ",
  ) %>%
  cols_merge(
    columns = c("term_organic_count", "term_organic_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_natural_count", "term_natural_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_chemfree_count", "term_chemfree_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_pestfree_count", "term_pestfree_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_bioprod_count", "term_bioprod_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_bio_count", "term_bio_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_eco_count", "term_eco_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_gmo_count", "term_gmo_perc"),
    pattern = "{1} ({2})"
  ) %>%
  #cols_merge(
  #  columns = c("term_dontknow_count", "term_dontknow_perc"),
  #  pattern = "{1} ({2})"
  #) %>%
  fmt_percent(
    columns = c(term_organic_perc, term_natural_perc, term_chemfree_perc,
                term_pestfree_perc, term_bioprod_perc, term_bio_perc,
                term_eco_perc, term_gmo_perc),
    decimals = 0
  ) %>%
  tab_header(
    title = "Table 6 - Brazil"
  ) %>%
  grand_summary_rows(
    columns = c(org_count, term_organic_count, term_natural_count, term_chemfree_count,
                term_pestfree_count, term_bioprod_count, term_bio_count,
                term_eco_count, term_gmo_count),
    fns = list(total = ~sum(., na.rm = TRUE)),
    formatter = fmt_number,
    decimals = 0,
  ) %>%
  sub_missing() 

# Display the table
tab6_categories_brazil

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 6 - Brazil")
writeData(table_outputs, sheet = "Table 6 - Brazil", x = tab6_categories_brazil)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```


##### India

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Create new instance of dataset for Table 6 - India
tab6_data_india <- tab6_data %>%
  filter(country == "India")

# PRODUCT-LEVEL SUMMARY

# Vector of product abbreviations
products <- c("tom", "leaf", "ban", "man", "fj", "milk", "cof", "tea", "mill", "chic", "daal", "wht", "rice", "nut")

# Define a function to summarize data for a given product and dataset
tab6_product_fn_india <- function(product) {
  tab6_data_india %>%
    summarise(
      org_count = sum(get(paste0(product, "_org")) == "Yes", na.rm = TRUE),
      term_organic_count = sum(get(paste0(product, "_org_terms_Organic")) == 1, na.rm = TRUE),
      term_organic_perc = term_organic_count / org_count,
      term_natural_count = sum(get(paste0(product, "_org_terms_Natural")) == 1, na.rm = TRUE),
      term_natural_perc = term_natural_count / org_count,
      term_chemfree_count = sum(get(paste0(product, "_org_terms_Chemical-free")) == 1, na.rm = TRUE),
      term_chemfree_perc = term_chemfree_count / org_count,
      term_pestfree_count = sum(get(paste0(product, "_org_terms_Pesticide-free")) == 1, na.rm = TRUE),
      term_pestfree_perc = term_pestfree_count / org_count,
      term_bioprod_count = sum(get(paste0(product, "_org_terms_Bioproducts")) == 1, na.rm = TRUE),
      term_bioprod_perc = term_bioprod_count / org_count,
      term_bio_count = sum(get(paste0(product, "_org_terms_Bio")) == 1, na.rm = TRUE),
      term_bio_perc = term_bio_count / org_count,
      term_eco_count = sum(get(paste0(product, "_org_terms_Eco")) == 1, na.rm = TRUE),
      term_eco_perc = term_eco_count / org_count,
      term_gmo_count = sum(get(paste0(product, "_org_terms_GMO-free")) == 1, na.rm = TRUE),
      term_gmo_perc = term_gmo_count / org_count,
      #term_dontknow_count = sum(get(paste0(product, "_org_terms_Don't know")) == 1, na.rm = TRUE),
      #term_dontknow_perc = term_dontknow_count / org_count
    ) %>%
    mutate(
      product = product,
      category = case_when(product %in% c("fj", "milk", "cof", "tea") ~ "beverages",
                           product %in% c("tom", "leaf", "ban", "man") ~ "fresh produce",
                           TRUE ~ "other")
    ) %>% 
    select(category, product, everything())
}

# Apply the function to each product and combine the results
product_summary_list_india <- lapply(products, tab6_product_fn_india)
tab6_product_summary_india <- bind_rows(product_summary_list_india)

## CATEGORY-LEVEL SUMMARY

tab6_category_summary_india <- tab6_product_summary_india %>%
  group_by(category) %>%
  summarise(
    org_count = sum(org_count, na.rm = TRUE),
    term_organic_count = sum(term_organic_count, na.rm = TRUE),
    term_organic_perc = mean(term_organic_perc, na.rm = TRUE),
    term_natural_count = sum(term_natural_count, na.rm = TRUE),
    term_natural_perc = mean(term_natural_perc, na.rm = TRUE),
    term_chemfree_count = sum(term_chemfree_count, na.rm = TRUE),
    term_chemfree_perc = mean(term_chemfree_perc, na.rm = TRUE),
    term_pestfree_count = sum(term_pestfree_count, na.rm = TRUE),
    term_pestfree_perc = mean(term_pestfree_perc, na.rm = TRUE),
    term_bioprod_count = sum(term_bioprod_count, na.rm = TRUE),
    term_bioprod_perc = mean(term_bioprod_perc, na.rm = TRUE),
    term_bio_count = sum(term_bio_count, na.rm = TRUE),
    term_bio_perc = mean(term_bio_perc, na.rm = TRUE),
    term_eco_count = sum(term_eco_count, na.rm = TRUE),
    term_eco_perc = mean(term_eco_perc, na.rm = TRUE),
    term_gmo_count = sum(term_gmo_count, na.rm = TRUE),
    term_gmo_perc = mean(term_gmo_perc, na.rm = TRUE),
    #term_dontknow_count = sum(term_dontknow_count, na.rm = TRUE),
    #term_dontknow_perc = mean(term_dontknow_perc, na.rm = TRUE)
  )


# Create gt table
tab6_categories_india <- tab6_category_summary_india %>%
  gt() %>%
  cols_label(
    category = "Category",
    org_count = "Total organic products",
    term_organic_count = "Organic, n(%)",
    term_organic_perc = " ",
    term_natural_count = "Natural, n(%)",
    term_natural_perc = " ",
    term_chemfree_count = "Chemical-free, n(%)",
    term_chemfree_perc = " ",
    term_pestfree_count = "Pesticide-free, n(%)",
    term_pestfree_perc = " ",
    term_bioprod_count = "Bioproduct, n(%)",
    term_bioprod_perc = " ",
    term_bio_count = "Bio, n(%)",
    term_bio_perc = " ",
    term_eco_count = "Eco, n(%)",
    term_eco_perc = " ",
    term_gmo_count = "GMO-free, n(%)",
    term_gmo_perc = " ",
    #term_dontknow_count = "Don't know, n(%)",
    #term_dontknow_perc = " ",
  ) %>%
  cols_merge(
    columns = c("term_organic_count", "term_organic_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_natural_count", "term_natural_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_chemfree_count", "term_chemfree_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_pestfree_count", "term_pestfree_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_bioprod_count", "term_bioprod_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_bio_count", "term_bio_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_eco_count", "term_eco_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_gmo_count", "term_gmo_perc"),
    pattern = "{1} ({2})"
  ) %>%
  #cols_merge(
  #  columns = c("term_dontknow_count", "term_dontknow_perc"),
  #  pattern = "{1} ({2})"
  #) %>%
  fmt_percent(
    columns = c(term_organic_perc, term_natural_perc, term_chemfree_perc,
                term_pestfree_perc, term_bioprod_perc, term_bio_perc,
                term_eco_perc, term_gmo_perc),
    decimals = 0
  ) %>%
  tab_header(
    title = "Table 6 - India"
  ) %>%
  grand_summary_rows(
    columns = c(org_count, term_organic_count, term_natural_count, term_chemfree_count,
                term_pestfree_count, term_bioprod_count, term_bio_count,
                term_eco_count, term_gmo_count),
    fns = list(total = ~sum(., na.rm = TRUE)),
    formatter = fmt_number,
    decimals = 0,
  ) %>%
  sub_missing() 

# Display the table
tab6_categories_india

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 6 - India")
writeData(table_outputs, sheet = "Table 6 - India", x = tab6_categories_india)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```



##### UK

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Create new instance of dataset for Table 6 - UK
tab6_data_uk <- tab6_data %>%
  filter(country == "UK")

# PRODUCT-LEVEL SUMMARY

# Vector of product abbreviations
products <- c("tom", "leaf", "ban", "man", "fj", "milk", "cof", "tea", "mill", "chic", "daal", "wht", "rice", "nut")

# Define a function to summarize data for a given product and dataset
tab6_product_fn_uk <- function(product) {
  tab6_data_uk %>%
    summarise(
      org_count = sum(get(paste0(product, "_org")) == "Yes", na.rm = TRUE),
      term_organic_count = sum(get(paste0(product, "_org_terms_Organic")) == 1, na.rm = TRUE),
      term_organic_perc = term_organic_count / org_count,
      term_natural_count = sum(get(paste0(product, "_org_terms_Natural")) == 1, na.rm = TRUE),
      term_natural_perc = term_natural_count / org_count,
      term_chemfree_count = sum(get(paste0(product, "_org_terms_Chemical-free")) == 1, na.rm = TRUE),
      term_chemfree_perc = term_chemfree_count / org_count,
      term_pestfree_count = sum(get(paste0(product, "_org_terms_Pesticide-free")) == 1, na.rm = TRUE),
      term_pestfree_perc = term_pestfree_count / org_count,
      term_bioprod_count = sum(get(paste0(product, "_org_terms_Bioproducts")) == 1, na.rm = TRUE),
      term_bioprod_perc = term_bioprod_count / org_count,
      term_bio_count = sum(get(paste0(product, "_org_terms_Bio")) == 1, na.rm = TRUE),
      term_bio_perc = term_bio_count / org_count,
      term_eco_count = sum(get(paste0(product, "_org_terms_Eco")) == 1, na.rm = TRUE),
      term_eco_perc = term_eco_count / org_count,
      term_gmo_count = sum(get(paste0(product, "_org_terms_GMO-free")) == 1, na.rm = TRUE),
      term_gmo_perc = term_gmo_count / org_count,
      #term_dontknow_count = sum(get(paste0(product, "_org_terms_Don't know")) == 1, na.rm = TRUE),
      #term_dontknow_perc = term_dontknow_count / org_count
    ) %>%
    mutate(
      product = product,
      category = case_when(product %in% c("fj", "milk", "cof", "tea") ~ "beverages",
                           product %in% c("tom", "leaf", "ban", "man") ~ "fresh produce",
                           TRUE ~ "other")
    ) %>% 
    select(category, product, everything())
}

# Apply the function to each product and combine the results
product_summary_list_uk <- lapply(products, tab6_product_fn_uk)
tab6_product_summary_uk <- bind_rows(product_summary_list_uk)

## CATEGORY-LEVEL SUMMARY

tab6_category_summary_uk <- tab6_product_summary_uk %>%
  group_by(category) %>%
  summarise(
    org_count = sum(org_count, na.rm = TRUE),
    term_organic_count = sum(term_organic_count, na.rm = TRUE),
    term_organic_perc = mean(term_organic_perc, na.rm = TRUE),
    term_natural_count = sum(term_natural_count, na.rm = TRUE),
    term_natural_perc = mean(term_natural_perc, na.rm = TRUE),
    term_chemfree_count = sum(term_chemfree_count, na.rm = TRUE),
    term_chemfree_perc = mean(term_chemfree_perc, na.rm = TRUE),
    term_pestfree_count = sum(term_pestfree_count, na.rm = TRUE),
    term_pestfree_perc = mean(term_pestfree_perc, na.rm = TRUE),
    term_bioprod_count = sum(term_bioprod_count, na.rm = TRUE),
    term_bioprod_perc = mean(term_bioprod_perc, na.rm = TRUE),
    term_bio_count = sum(term_bio_count, na.rm = TRUE),
    term_bio_perc = mean(term_bio_perc, na.rm = TRUE),
    term_eco_count = sum(term_eco_count, na.rm = TRUE),
    term_eco_perc = mean(term_eco_perc, na.rm = TRUE),
    term_gmo_count = sum(term_gmo_count, na.rm = TRUE),
    term_gmo_perc = mean(term_gmo_perc, na.rm = TRUE),
    #term_dontknow_count = sum(term_dontknow_count, na.rm = TRUE),
    #term_dontknow_perc = mean(term_dontknow_perc, na.rm = TRUE)
  )


# Create gt table
tab6_categories_uk <- tab6_category_summary_uk %>%
  gt() %>%
  cols_label(
    category = "Category",
    org_count = "Total organic products",
    term_organic_count = "Organic, n(%)",
    term_organic_perc = " ",
    term_natural_count = "Natural, n(%)",
    term_natural_perc = " ",
    term_chemfree_count = "Chemical-free, n(%)",
    term_chemfree_perc = " ",
    term_pestfree_count = "Pesticide-free, n(%)",
    term_pestfree_perc = " ",
    term_bioprod_count = "Bioproduct, n(%)",
    term_bioprod_perc = " ",
    term_bio_count = "Bio, n(%)",
    term_bio_perc = " ",
    term_eco_count = "Eco, n(%)",
    term_eco_perc = " ",
    term_gmo_count = "GMO-free, n(%)",
    term_gmo_perc = " ",
    #term_dontknow_count = "Don't know, n(%)",
    #term_dontknow_perc = " ",
  ) %>%
  cols_merge(
    columns = c("term_organic_count", "term_organic_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_natural_count", "term_natural_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_chemfree_count", "term_chemfree_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_pestfree_count", "term_pestfree_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_bioprod_count", "term_bioprod_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_bio_count", "term_bio_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_eco_count", "term_eco_perc"),
    pattern = "{1} ({2})"
  ) %>%
  cols_merge(
    columns = c("term_gmo_count", "term_gmo_perc"),
    pattern = "{1} ({2})"
  ) %>%
  #cols_merge(
  #  columns = c("term_dontknow_count", "term_dontknow_perc"),
  #  pattern = "{1} ({2})"
  #) %>%
  fmt_percent(
    columns = c(term_organic_perc, term_natural_perc, term_chemfree_perc,
                term_pestfree_perc, term_bioprod_perc, term_bio_perc,
                term_eco_perc, term_gmo_perc),
    decimals = 0
  ) %>%
  tab_header(
    title = "Table 6 - UK"
  ) %>%
  grand_summary_rows(
    columns = c(org_count, term_organic_count, term_natural_count, term_chemfree_count,
                term_pestfree_count, term_bioprod_count, term_bio_count,
                term_eco_count, term_gmo_count),
    fns = list(total = ~sum(., na.rm = TRUE)),
    formatter = fmt_number,
    decimals = 0,
  ) %>%
  sub_missing() 

# Display the table
tab6_categories_uk

# Export to table_outputs workbook
addWorksheet(table_outputs, "Table 6 - UK")
writeData(table_outputs, sheet = "Table 6 - UK", x = tab6_categories_uk)
saveWorkbook(table_outputs, "C:/Users/s1985751/Documents/GitHub/fea/table_outputs.xlsx", overwrite = TRUE)

```



### Brands - Table 7

```{r echo = FALSE, message = FALSE, warning = FALSE}

# vector with brand names variables
vector_brandnames <- data_clean %>% 
  select(contains("brand_new")) %>%
  names()

table7 <- left_join(
  # number of brands in each sentinel food
  data_clean %>%
    select(country, vector_brandnames) %>%
    pivot_longer(cols = c(vector_brandnames), 
                 names_to = "food", 
                 values_to = "brand") %>%
    filter(!is.na(brand)) %>%
    group_by(country, food) %>%
    summarise(n_brands = n()),
  
  # top three brands for each sentinel food
  data_clean %>%
    select(country, vector_brandnames) %>%
    pivot_longer(cols = c(vector_brandnames), 
                 names_to = "food", 
                 values_to = "brand") %>%
    filter(!is.na(brand)) %>%
    group_by(country, food) %>%
    count(brand) %>%
    arrange(desc(n), .by_group = TRUE) %>%
    slice(1:3) %>%
    mutate(rank = row_number())
) %>%
  # adjust variables
  mutate(food = paste(food, rank),
         perc = round(n/n_brands*100,2),
         brand = paste0(brand, " (", n, ", ", perc, "%)")) %>%
  select(country, food, brand) %>%
  # reshape table to match the analysis plan
  pivot_wider(names_from = country,
              values_from = brand)

kable(table7)
```



### Certification - Table 8

```{r echo = FALSE, message = FALSE, warning = FALSE}

# values per country
country <- data_clean %>%
  group_by(country) %>%
  summarise(Certified = sum(cert_count),
            Total = sum(org_foods_count)) %>%
  mutate(Proportion = round(Certified/Total*100, 2)) %>%
  rename()

# values per store type
vendortype <- data_clean %>%
  group_by(vendor_type)%>%
  summarise(Certified = sum(cert_count),
            Total = sum(org_foods_count)) %>%
  mutate(Proportion = round(Certified/Total*100, 2))


# values per food
products <- c("tom", "leaf", "ban", "man", "fj", "milk", "cof", "tea", "mill", "chic", "daal", "wht", "rice", "nut")
vector_organics <- paste0(products, "_org")
vector_cert <- paste0(products, "_cert")


sentinelfood <- cbind(
  # count certifications
  data_clean %>%
    select(id, country, all_of(vector_cert)) %>%
    pivot_longer(cols = c(vector_cert), 
                 names_to = "food", 
                 values_to = c("certified")) %>%
    group_by(food) %>%
    summarise(Certified = sum(certified >= 1, na.rm=T)),
  
  # count all organics
  data_clean %>%
    select(id, country, all_of(vector_organics)) %>%
    pivot_longer(cols = c(vector_organics), 
                 names_to = "food", 
                 values_to = c("total")) %>%
    group_by(food) %>%
    summarise(Total = sum(total == "Yes", na.rm=T)) %>%
    select(-food)
) %>%
  mutate(Proportion = round(Certified/Total*100, 2))

kable(country)
kable(vendortype)
kable(sentinelfood)
```










